\documentclass[10pt]{resume}
\usepackage[left=0.45in,top=0.3in,right=0.45in,bottom=0.3in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=1pt, left=0.8em}

\setlength{\parskip}{1.5pt}
\setlength{\parsep}{0pt}
\renewcommand{\baselinestretch}{1.0}

\name{Shashwat Nath}
\address{shashwatnath30@gmail.com \quad +91 8810614670 \quad Delhi, India}
\address{\href{https://live-portfolio-3d.onrender.com}{Portfolio} \quad
\href{https://github.com/Magmastorm3007}{GitHub} \quad
\href{https://leetcode.com/u/user5454Z}{LeetCode} \quad
\href{https://magmastorm.hashnode.dev}{Blog}}

\begin{document}
\footnotesize

% -------------------- SUMMARY --------------------
\begin{rSection}{SUMMARY}
\textbf{Data \& Software Engineer} with nearly 2 years of experience designing and delivering cloud-native ETL pipelines, backend services, and real-time systems for high-security,  massive datasets in the insurance domain for a leading American Insurance firm. Skilled in \textbf{PySpark, AWS, Node.js, SQL}, with proven expertise in building production-ready data platforms, serverless workflows, and scalable dashboards. Strong track record of optimizing performance, ensuring compliance, and enhancing observability in enterprise environments, delivering measurable business impact.
\end{rSection}

% -------------------- EXPERIENCE --------------------
\begin{rSection}{EXPERIENCE}

\textbf{Data Engineer}, LTIMindTree \hfill Dec 2024–Present, Bengaluru
\begin{itemize}
  \item Migrated \textbf{50+} legacy ETL workflows from on-premise Informatica systems to \textbf{AWS Glue (PySpark)}, modernizing pipelines for a leading American insurance client and reducing monthly server costs by \textbf{38\%}.
  \item Built \textbf{serverless pipelines} using AWS Lambda and Step Functions (Python \& Node.js), streamlining event-driven data delivery and cutting software licensing costs by \textbf{20\%}.
  \item Tuned Spark configurations and partitioning strategies, achieving \textbf{30–50\%} faster execution while handling large-scale datasets.
  \item Monitored and maintained \textbf{100+} financial tables using Splunk and Stonebranch, implementing automated alerts and daily compliance reports.
  \item Integrated AWS \textbf{CloudFormation logs into Splunk dashboards} for real-time infrastructure and pipeline observability.
  \item Implemented data quality and code coverage checks using Pytest and SonarQube, ensuring \textbf{75\%+} coverage across ETL pipelines and backend Lambda services.
  \item Developed and maintained AWS DMS scripts to migrate databases and validate schemas across on-premise and cloud environments.
  \item Collaborated with cross-functional teams to deliver production-ready data services using Agile/Scrum and CI/CD pipelines.
\end{itemize}

\textbf{Software Developer Intern}, HumanAI Pvt. Ltd. \hfill Dec 2023–Jun 2024, Singapore (Remote)
\begin{itemize}
  \item Designed a scalable, responsive \textbf{React.js dashboard} to monitor multiple IoT installations, optimizing builds and systemd services to reduce RAM usage by 1GB.
  \item Developed a \textbf{GPT-4 powered Recipe Analyzer App} (Next.js) with caching optimizations, reducing   GPT API token usage hits by \textbf{30\%} and demonstrating AI-driven cost efficiency.
  \item Built Web3 applications to interact with smart contracts on \textbf{Hyperledger Besu}, enabling secure and verified blockchain data visualization.
  \item Collaborated with clients to test, document, and improve REST APIs, accelerating feature delivery and improving overall system reliability.
\end{itemize}


% -------------------- PROJECTS --------------------
\begin{rSection}{PROJECTS}

\textbf{Samagra Shiksha Dashboard — Software Developer (Contract)} \hfill Jul–Nov 2024, Remote
\begin{itemize}
    \item Developed a fully responsive \textbf{Education Analytics Dashboard} prototype with role-based access control (RBAC), monitoring, and reporting features; piloted with 200 users, enabling learning facilitators to manage and track educational outcomes effectively.
    \item Deployed the platform on \textbf{DigitalOcean} with \textbf{MongoDB Atlas}, architected for seamless scalability to 100k+ users while ensuring secure API access, data compliance, and high availability for education stakeholders.
\end{itemize}

\textbf{Set Memory (NPM)} — Published CLI tool to auto-tune Node.js memory limits (\textbf{500+ downloads}).  
\href{https://www.npmjs.com/package/set-memory}{[NPM]}

\end{rSection}

% -------------------- EDUCATION --------------------
\begin{rSection}{EDUCATION}
\textbf{B.Tech, Information Technology} \hfill Manipal University Jaipur \\
2020–2024 \quad CGPA: \textbf{8.53}
\end{rSection}

% -------------------- RESEARCH --------------------
\begin{rSection}{RESEARCH}
\begin{itemize}
  \item Published paper with \textbf{Springer}: “Analysis of Breast Cancer Detection Algorithms using ML” (SVM, KNN, Random Forest).  
  \href{https://link.springer.com/chapter/10.1007/978-981-19-4990-6_57}{[Link]} — Received Best Paper recognition at ICICC 2022.
  \item Ongoing research: \textbf{Hybrid Genetic Algorithm for Whale and Gravitational Search Optimization} for feature selection in ML models.
\end{itemize}
\end{rSection}

% -------------------- CERTIFICATIONS --------------------
\begin{rSection}{CERTIFICATIONS}
\begin{itemize}
  \item \textbf{AWS Certified Developer – Associate} (Ongoing) — Gaining hands-on expertise in designing, deploying, and monitoring serverless and event-driven cloud applications, including AWS Glue, Lambda, Step Functions, and S3.
  \item \textbf{Oracle Database Foundations – Oracle Academy} — SQL programming, relational modeling, and performance-tuned design.
  \item \textbf{Red Hat System Administration II – Red Hat Academy} — Linux server administration, shell scripting, and monitoring.
\end{itemize}
\end{rSection}

% -------------------- SKILLS --------------------
\begin{rSection}{SKILLS}
\textbf{Languages:} C++,Python,JavaScript (Node.js), SQL \\
\textbf{Data Engineering:} PySpark, Airflow, ETL with AWS Glue, Lambda, Step Functions, DMS ,PostgreSQL\\
\textbf{Backend:} FastAPI, Express.js, Node.js,HyperLedger \\
\textbf{Cloud \& Big Data:} AWS (S3, Athena,Lambda,Glue,Step Functions,CloudWatch,SQS,SNS), Kafka,Digital Ocean(Droplet),Dbeaver \\
\textbf{DevOps \& Infra:} Docker, Kubernetes, Terraform, GitHub Actions, Jenkins \\
\textbf{Testing \& Monitoring:} Pytest, SonarQube, Splunk,Mocha,Jest
\end{rSection}

\end{document}
